\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-10 Paper_honeypot.tex
Eerste aanpassing layout & packages toegevoegd

%-------------------------------- Title ----------------------------------

@@

\begin{itemize}
\item   2206 root
\item     39 admin
\item     26 bin
\item     20 w000t
\item     19 oracle
\item     19 jenny
\end{itemize}

@@

\begin{itemize}
\item     55 
\item     28 123456
\item     20 111111
\item     16 root
\item     16 admin
\end{itemize}

@@

These 404's are interesting because they show us what adresses the attackers were trying to access. For instance, we see a lot of scans for phpMyAdmin (phpMyAdmin-3.3.10.5, phpMyAdmin-3.4.7, phpMyAdmin-3.4.6 etcetera). They also searched non existing folders for these phpMyAdmin files.

Also serveral client IDs are visible in these logs: "\verbatim{"-"}", which is a blank user/client ID, (3432 attempts), "MiRRORS" (310 attempts), "ZmEu" (41 attempts) and "Morfeus Fucking Scanner" (4 attempts). These seem to be search engine crawlers. It is interesting to see that both several "\verbatim{"-"}" and several "ZmEu" users are scanning for "/w00tw00t.at.blackhats.romanian.anti-sec:)" and "/w00tw00t.at.ISC.SANS.DFind:)". The attackers using "ZmEu" found one valid path: /phpmyadmin/, however he did not exploit this. "Morfeus Fucking Scanner" was used by one attacker, that soly searched for /user/soapCaller.bs. We could not find anything on this .bs file. We expected to see several occurances of "/robots.txt" because this is a common way to start when using a search engine crawler, but none were found.

>>>>

\usepackage{booktabs}
\usepackage[parfill]{parskip}
%-------------------------------- Title ----------------------------------

@@

\begin{tabular}{|l|r|}
\hline
2206 & root \\ \hline
39 & admin \\ \hline
26 & bin \\ \hline
20 & w000t \\ \hline
19 & oracle \\ \hline
19 & jenny \\ \hline
\end{tabular}

@@

\begin{tabular}{|l|r|}
\hline
55 &  \\ \hline
28 & 123456 \\ \hline
20 & 111111 \\ \hline
16 & root \\ \hline
16 & admin \\ \hline
\end{tabular}

@@

These 404's are interesting because they show us what addresses the attackers were trying to access. For instance, we see a lot of scans for phpMyAdmin (phpMyAdmin-3.3.10.5, phpMyAdmin-3.4.7, phpMyAdmin-3.4.6 etcetera). They also searched non existing folders for these phpMyAdmin files.

Also serveral client IDs are visible in these logs:

\begin{itemize}
\item ``\emph{``-''}'' (3432 attempts)

This is a blank user/client ID.

\item ``MiRRORS'' (310 attempts)

\tocheck{Info over MiRRORS}

\item ``ZmEu'' (41 attempts)

The attackers using ``ZmEu'' found one valid path: /phpmyadmin/, however he did not exploit this. It is interesting to see that both several ``\emph{''-''}'' and several ``ZmEu'' users are scanning for ``/w00tw00t.at.blackhats.romanian.anti-sec:)'' and ``/w00tw00t.at.ISC.SANS.DFind:)''

\item ``Morfeus Fucking Scanner'' (4 attempts)

``Morfeus Fucking Scanner'' was used by one attacker, that soly searched for /user/soapCaller.bs. We could not find anything on this .bs file.
\end{itemize}

We expected to see several occurances of ``/robots.txt'' because this is a common way to start when using a search engine crawler, but none were found.
